SEER Medicaid

### 2023-09-27 Manuscript Analysis code 0 to 19.Rmd
Deleted some unecessary code from 60 month survival percentage calculations

@@

```{r}
pdf("Figure 2.pdf", width=8.5, height=11, paper="USr")
Plot1 + Plot2 + Plot3 + Plot4 + plot_layout(ncol=2, nrow=2, guides='collect') &
  theme(legend.position='bottom')

@@

dev.off()
```
# SUPPLEMENTARY TABLE 2: Estimate survival time 0 to 19 at 160 mo
```{r}
# Overall
summary(survfit(Surv(fumo, can_dead) ~ 1, data = seer0to19), times=60) # estimates 60 month survival time

@@

# SUPPLEMENTARY TABLE 3: Populate a table with survival by age group at 60 mo
```{r}
age <- unique(seer0to19$age_cat)
# In_Medicaid_Flag
results <- data.frame(matrix(ncol=6, nrow=0)) #create the table
columns<-c("Medicaid_Category", "Time (months)", "Survival Percentage",  "LowerCI", "UpperCI", "Age_cat") # label the columns with names
colnames(results)<-columns

@@

# mcont66
# calculate survival at 60 mo
results <- data.frame(matrix(ncol=6, nrow=0)) #create the table
columns<-c("Medicaid_Category", "Time (months)","Survival Percentage",  "LowerCI", "UpperCI", "Age_cat") #label the columns with names
colnames(results)<-columns

for (i in age) {
  df<- seer0to19 %>% 
    filter(age_cat == i)
  x<-summary(survfit(Surv(fumo, can_dead) ~ mcont66, df), times=60)
  results2 <- data.frame(matrix(ncol=4, nrow=0)) # create the table
  columns<-c("Medicaid_Category", "Survival Percentage",  "LowerCI", "UpperCI") #label the columns with names
  colnames(results2)<-columns
  results2[1:4,]<-c(x$strata, round(x$surv,3)*100, round(x$lower,3)*100 , round(x$upper,3)*100)
  results2$Group<- i
  results <-rbind(results, results2)
}

@@

# In_Medicaid_Flag
# calculate survival at 60 mo
results <- data.frame(matrix(ncol=5, nrow=0)) # create the table
columns<-c("Medicaid_Category", "Survival Percentage",  "LowerCI", "UpperCI", "Race_ethnicity") #label the columns with names
colnames(results)<-columns

@@

# mcont66
# calculate survival at 60 mo
results <- data.frame(matrix(ncol=5, nrow=0)) #create the table
columns<-c("Medicaid_Category", "Survival Percentage",  "LowerCI", "UpperCI", "Race_ethnicity") #label the columns with names
colnames(results)<-columns

@@

# In_Medicaid_Flag
# calculate survival at 60 mo
results <- data.frame(matrix(ncol=5, nrow=0)) # create the table
columns<-c("Medicaid_Category", "Survival Percentage",  "LowerCI", "UpperCI", "Cancer_type") #label the columns with names
colnames(results)<-columns

@@

# mcont66
# calculate survival at 60 mo
results <- data.frame(matrix(ncol=5, nrow=0)) # create the table
columns<-c("Medicaid_Category", "Survival Percentage",  "LowerCI", "UpperCI", "Cancer_type") # label the columns with names
colnames(results)<-columns

@@

SuppTable7c <- rbind(a,b,c,d,f,h,i,j,k, m,n,o,p,r,s,t,u,v,w)
```

>>>>

# test code
```{r}

# create categories for AYA codes
class(seer0to39$AYA_site_recode_WHO_2008) # numeric

seer0to39 <- seer0to39 %>%
  mutate(can_typeAYA = case_when(AYA_site_recode_WHO_2008 %in% c(1,2,3,4) ~ 0,
                                 AYA_site_recode_WHO_2008 %in% c(5,6) ~ 1,
                                 AYA_site_recode_WHO_2008 %in% c(7,8,9,10,11,12,13,14,15,16) ~ 2,
                                 AYA_site_recode_WHO_2008 %in% c(17,18,19,20) ~ 3,
                                 AYA_site_recode_WHO_2008 %in% c(21,22,23,24,25) ~ 4,
                                 AYA_site_recode_WHO_2008 %in% c(26,27,28) ~ 5,
                                 AYA_site_recode_WHO_2008 %in% c(29,30) ~ 6,
                                 AYA_site_recode_WHO_2008 %in% c(31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48) ~ 7,
                                 AYA_site_recode_WHO_2008 %in% c(49,50,51,52,53,54,55) ~ 8,
                                 AYA_site_recode_WHO_2008 %in% c(55,56) ~ 9,
                                 AYA_site_recode_WHO_2008 == 99 ~ 10))

seer0to39$can_typeAYA <- factor(seer0to39$can_typeAYA, levels = c(0:10), labels = c(
  "1. Leukemias",
  "2. Lymphomas",
  "3. CNS and Other Intracranial and Intraspinal Neoplasms (all behaviors)",
  "4. Osseous & Chondromatous Neoplasms",
  "5. Soft Tissue Sarcomas",
  "6. Germ Cell and Trophoblastic Neoplasms",
  "7. Melanoma and Skin Carcinomas",
  "8. Carcinomas",
  "9. Miscellaneous specified neoplasms, NOS",
  "10. Unspecified Malignant Neoplasms",
  "Unclassified"))
table(seer0to39$can_typeAYA, useNA = "always")

# categorize brain tumors according to AYA definition

seer0to39 <- seer0to39 %>%
  mutate(brain = case_when (can_typeAYA == "3. CNS and Other Intracranial and Intraspinal Neoplasms (all behaviors)"  & AYA_site_recode_WHO_2008 %in% c(7,8,9) ~ 0, # 3.1 Astrocytoma
                            can_typeAYA == "3. CNS and Other Intracranial and Intraspinal Neoplasms (all behaviors)" & AYA_site_recode_WHO_2008 %in% c(10) ~ 1, # 3.2 Other glioma
                            can_typeAYA == "3. CNS and Other Intracranial and Intraspinal Neoplasms (all behaviors)" & AYA_site_recode_WHO_2008 %in% c(11) ~ 2, # 3.3 Ependymoma
                            can_typeAYA == "3. CNS and Other Intracranial and Intraspinal Neoplasms (all behaviors)" & AYA_site_recode_WHO_2008 %in% c(12,13) ~ 3, # 3.4 Medulloblastoma and other PNET
                            can_typeAYA == "3. CNS and Other Intracranial and Intraspinal Neoplasms (all behaviors)" & AYA_site_recode_WHO_2008 %in% c(14) ~ 4, # 3.5 Other specified intracranial and instraspinal neoplasms
                            can_typeAYA == "3. CNS and Other Intracranial and Intraspinal Neoplasms (all behaviors)" & AYA_site_recode_WHO_2008 %in% c(15,16) ~ 5)) # 3.6 Unspecified intracranial and intraspinal neoplasms
seer0to39$brain
table(seer0to39$brain, useNA = "always")

seer0to39$brain <- factor(seer0to39$brain, levels = c(0:5), labels = c(
  "3.1 Astrocytoma",
  "3.2 Other glioma",
  "3.3 Ependymoma",
  "3.4 Medulloblastoma and other PNET",
  "3.5 Other specified intracranial and instraspinal neoplasms",
  "3.6 Unspecified intracranial and intraspinal neoplasms"))
table(seer0to39$brain, useNA = "always")

df <- seer0to39 %>%
  filter(can_type == "III. CNS and miscellaneous intracranial and intraspinal neoplasms"|can_typeAYA == "3. CNS and Other Intracranial and Intraspinal Neoplasms (all behaviors)") %>%
  group_by(can_type, can_typeAYA)%>%
  tally()
```

@@

```{r}
pdf("Figure 2.pdf", width=8.5, height=11, paper="USr")
Plot1 + Plot2 + Plot3 + Plot4 + plot_layout(ncol=2, nrow=2, guides='collect') &
  theme(legend.position='bottom')
dev.off()
```

@@

dev.off()
```
# SUPPLEMENTARY TABLE 2: Estimate survival time 0 to 19 at 60 mo
```{r}
# Overall
summary(survfit(Surv(fumo, can_dead) ~ 1, data = seer0to19), times=60) # estimates 60 month survival time

@@

# SUPPLEMENTARY TABLE 3: Populate a table with survival by age group at 60 mo
```{r}
age <- unique(seer0to19$age_cat)

# In_Medicaid_Flag
results <- data.frame(matrix(ncol=4, nrow=0)) #create the table
columns<-c("Medicaid Category", "Survival Percentage",  "LowerCI", "UpperCI") # label the columns with names
colnames(results)<-columns

@@

# mcont66
# calculate survival at 60 mo
results <- data.frame(matrix(ncol=4, nrow=0)) #create the table
columns<-c("Medicaid_Category", "Survival Percentage",  "LowerCI", "UpperCI") # label the columns with names
colnames(results)<-columns

for (i in age) {
  df<- seer0to19 %>% 
    filter(age_cat == i)
  x<-summary(survfit(Surv(fumo, can_dead) ~ mcont66, df), times=60)
  results2 <- data.frame(matrix(ncol=4, nrow=0)) # create the table
  columns<-c("Medicaid_Category", "Survival Percentage",  "LowerCI", "UpperCI") # label the columns with names
  colnames(results2)<-columns
  results2[1:4,]<-c(x$strata, round(x$surv,3)*100, round(x$lower,3)*100 , round(x$upper,3)*100)
  results2$Group<- i
  results <-rbind(results, results2)
}

@@

# In_Medicaid_Flag
# calculate survival at 60 mo
results <- data.frame(matrix(ncol=4, nrow=0)) # create the table
columns<-c("Medicaid_Category", "Survival Percentage",  "LowerCI", "UpperCI") #label the columns with names
colnames(results)<-columns

@@

# mcont66
# calculate survival at 60 mo
results <- data.frame(matrix(ncol=5, nrow=0)) #create the table
columns<-c("Medicaid_Category", "Survival Percentage",  "LowerCI", "UpperCI") #label the columns with names
colnames(results)<-columns

@@

# In_Medicaid_Flag
# calculate survival at 60 mo
results <- data.frame(matrix(ncol=4, nrow=0)) # create the table
columns<-c("Medicaid_Category", "Survival Percentage",  "LowerCI", "UpperCI") #label the columns with names
colnames(results)<-columns

@@

# mcont66
# calculate survival at 60 mo
results <- data.frame(matrix(ncol=4, nrow=0)) # create the table
columns<-c("Medicaid_Category", "Survival Percentage",  "LowerCI", "UpperCI") # label the columns with names
colnames(results)<-columns

@@

SuppTable7c <- rbind(a,b,c,d,f,h,i,j,k, m,n,o,p,r,s,t,u,v,w)
